Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-01-20 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
CAV 2020 paper update

Here, we have developed a (non-trivial) variant of counterexample guided inductive synthesis (CEGIS) for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data. Given a correctness specification $\sigma$, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability. In particular, on each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost. The candidate solution is then verified via symbolic model checking with a lower bound that serves as the minimum cost of reference; if the verification step does not fail, the lower bound is adjusted. If it fails, then a counterexample is provided with an optimal sizing that meets both power reliability and system cost. Here our focus is not on new criteria or even optimization objectives. Instead, our novelty relies on a practical approach to the pursuit of the optimal solution of PV systems using formal methods.

@@

%---------------------------------------------------------------------------
\subsection{Results}
%---------------------------------------------------------------------------

A Table with the details of the results is present on-line\footnote{\url{https://drive.google.com/file/d/1I1Cg4FNz9grMqXHUmOKnd-\_PFmLpmk6m/view?usp=sharing}}. Summarizing,  CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): CPAchecker produced the results within the time limit, which varied from $2.24$ to $3.92$ hours. Only case study $7$ led to a \textit{time out} result in CPAchecker, i.e., it was not solved within $240$ minutes. The violation (SAT result) indicated in Table~\ref{tab1} is the $assert$ of Line $22$ at Algorithm~\ref{alg:verification-algorithm}. CBMC and ESBMC are unable to produce any conclusive result. Situations of \textit{time out} or \textit{out of memory} occurred; these results partially answer the \textit{EG2} and \textit{EG3} \textcolor{red}{why? explain it here...}.

HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$) within a time shorter than $30$ seconds, which was faster than the proposed automated synthesis tool (cf.~\textit{EG3}) \textcolor{red}{why do we need to publish our results then?}. HOME Pro was unable to simulate case study $3$ since it does not have the feature of adjusting the battery autonomy, i.e., the tool always tries to feed with electricity the given load during $365$ days/year \textcolor{red}{Does this feature add more complexity to our synthesis model? If so, we have to point it out here}.

Comparing the results between the formal synthesis with CPAchecker and HOMER Pro, we have observed that most results are quite similar in terms of technical solution and cost (cf. Table~\ref{tab1}) \textcolor{red}{If the results are quite similar and HOME Pro is faster, what is the purpose of our method here?}. Mainly related to LCC, the cost was very close in cases $1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%. Even adopting the same price per kW to the PV panels, inverters, and batteries, HOMER Pro does not use costs related to charge controllers, which were introduced into our synthesis model, thus making it more precise. \textcolor{red}{this sentence is unclear... Our premise to adopt a fixed annual cost for operation and maintenance is that it can produce some impact at this discrepancy; however, it is not significant since this annual cost is too small when compared to the resulting LCC value}. We have observed that there exists a vast divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than our synthesis tool, probably because of the operation and maintenance costs assumed by our approach were underestimated to that specific load \textcolor{red}{is it good or bad? the way you have written looks like HOME Pro is the best option}.

@@

For the inverters, HOMER Pro suggests a value in kW very close to the peak of every case study, and it is just a reference value and not a commercial value of the employed inverter. The proposed synthesis tool, however, presents inverters that are commercial and can be found off-the-shelf. Therefore, this feature is a PRO to the formal synthesis method. Concerning the charge controllers, HOMER Pro does not include it as an explicit equipment in its mathematical model, only the synthesis tool presents a commercial controller and includes it during the cost analysis. Therefore, the formal synthesis method presents more reliable results than HOMER Pro. Case study $7$ was not solved by the synthesis tool within the time limit established during the experimental phase. Case study $3$ was not possible to simulate in HOMER Pro, because its restriction does not allow one to set the battery autonomy, thus resting both without parameters to comparison.

@@

%------------------------------------
\section{Conclusion} 
%------------------------------------

\textcolor{red}{What is the novelty of our work? what are the impacts/relevance of our method to the society and formal methods community? How formal methods can improve the people's life? we should emphasize the relevance of the problem we solve and give numbers to show the efficiency of our approach if compared to HOME Pro.}

Our synthesis tool can present a solution, which is far detailed and closer to the commercial reality than the solution presented by HOMER Pro. In particular, our automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from datasheet of manufacturers, including the model of the component, nominal current, and voltage. In this respect, even the manufacturer's brand can be presented (\textcolor{red}{shall we add this table online?} in Table~\ref{tab1} it was removed to avoid some advertising).
%
% ---- Bibliography ----
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{trindadeThesis}
%

\end{document}

%\subsection{Design and Simulation of Solar PV systems}
%The design and validation of a PV system can be done by hand or with the aid of a software tool. In order to address different aspects of the PV system design, there are various software tools available in the literature~\cite{Rajanna,Rawat}.
%public domain and commercial software available for the PV market. 
%According to \cite{Brooks}, t
%%%%%%%%%%
%
%The capabilities of tools available in the literature range from simple solar resource and %energy production estimation, %to site survey and system design tools,
%to complex financial analysis and project optimization. At this study, the commercial simulation tool HOMER PRO was selected to be used at the case studies in order to be compared with the automated verification tools.

>>>>

Here, we have developed a (non-trivial) variant of counterexample guided inductive synthesis (CEGIS) for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data. Given a correctness specification $\sigma$, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability. In particular, on each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost. The candidate solution is then verified via symbolic model checking with a lower bound that serves as the minimum cost of reference; if the verification step does not fail, the lower bound is adjusted. If it fails, then a counterexample is provided with an optimal sizing that meets both power reliability and system cost. Here our focus is not on new criteria or even optimization objectives.

@@

%---------------------------------------------------------------------------
\subsection{Results}
%---------------------------------------------------------------------------
A Table with the details of the results is present on-line\footnote{\url{https://drive.google.com/file/d/1I1Cg4FNz9grMqXHUmOKnd-\_PFmLpmk6m/view?usp=sharing}}.

Related to the verifiers comparison, CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): CPAchecker produced the results within the time limit, which varied from $2.24$ to $3.92$ hours. Only case study $7$ led to a \textit{time out} result in CPAchecker, i.e., it was not solved within $240$ minutes. The violation (SAT result) indicated in on-line Table is the $assert$ of Line $22$ at Algorithm~\ref{alg:verification-algorithm}. CBMC and ESBMC are unable to produce any conclusive result. Situations of \textit{time out} or \textit{out of memory} occurred; these results partially answer the \textit{EG1} and \textit{EG2}, \textcolor{red}{because there are optimal solutions and CPAchecker presented the better comparative results among the verifiers}.

@@

For the inverters, HOMER Pro suggests a value in kW very close to the peak of every case study, and it is just a reference value and not a commercial value of the employed inverter. The proposed synthesis tool, however, presents inverters that are commercial and can be found off-the-shelf. Therefore, this feature is a PRO to the formal synthesis method. Concerning the charge controllers, HOMER Pro does not include it as an explicit equipment in its mathematical model, only the synthesis tool presents a commercial controller and includes it during the cost analysis. Therefore, the formal synthesis method presents more reliable results than HOMER Pro. Case study $7$ was not solved by the synthesis tool within the time limit established during the experimental phase. HOME Pro was unable to simulate case study $3$ since it does not have the feature of adjusting the battery autonomy, i.e., the tool always tries to feed with electricity the given load during $365$ days/year. \textcolor{red}{This lack of recourse is a limitation, because it is usual to establish the autonomy as a design requirement}.

In terms of performance, HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$) within a time shorter than $30$ seconds, which was faster than the proposed automated synthesis tool (cf.~\textit{EG3}) \textcolor{red}{but not so sound as our synthesis method}.

\textcolor{red}{Comparing the results between the formal synthesis with CPAchecker and HOMER Pro, we have observed that the cost was very close in cases $1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%. However, HOMER Pro does not use costs related to charge controllers, which were introduced into our synthesis model. This charge controller cost makes the synthesis approach more precise and real. It was observed that there exists a divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than our synthesis tool. However this case study does not have a deployed PV system in order to validate which result is the correct.}

@@

%------------------------------------
\section{Conclusion} 
%------------------------------------
\textcolor{red}{
Our novelty relies on a practical approach for to pursuit of the optimal solution of PV systems using formal methods. The use of formal synthesis has no precedent in literature, and we show that the results of our approach, using seven case studies, are promising.} 
%\textcolor{red}{What is the novelty of our work? what are the impacts/relevance of our method to the society and formal methods community? How formal methods can improve the people's life? we should emphasize the relevance of the problem we solve and give numbers to show the efficiency of our approach if compared to HOME Pro.}
Our synthesis tool can present a solution, which is far detailed and closer to the commercial reality than the solution presented by HOMER Pro, an state-of-the art simulation tool. The use of data from real deployed systems in Amazonas State, Brazil, were important in order to reach that conclusion. The battery autonomy feature of our synthesis approach is an advantage as well. In addition, our automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from datasheet of manufacturers, including the model of the component, nominal current, and voltage. These details are important for the owner of the system and aids the process of equipment purchase.
%
% ---- Bibliography ----
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{trindadeThesis}
%
\end{document}
%\subsection{Design and Simulation of Solar PV systems}
%The design and validation of a PV system can be done by hand or with the aid of a software tool. In order to address different aspects of the PV system design, there are various software tools available in the literature~\cite{Rajanna,Rawat}.
%public domain and commercial software available for the PV market. 
%According to \cite{Brooks}, t
%%%%%%%%%%
%
%The capabilities of tools available in the literature range from simple solar resource and %energy production estimation, %to site survey and system design tools,
%to complex financial analysis and project optimization. At this study, the commercial simulation tool HOMER PRO was selected to be used at the case studies in order to be compared with the automated verification tools.
